\chapter{Research Question \&
Hypothesis}\label{research-question-hypothesis}

\subsection{Research questions}\label{research-questions}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  How much numerical diffusion and or dispersion does the D-Flow FM
  model produce when simulating a 3D lock-exchange experiment dependent?

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    What is the order of errors produced by D-Flow FM as a result of
    numerical diffusion and/or dispersion?
  \item
    How sensitive is the accuracy of the D-Flow FM model to time, space
    and numerically related parameters?
  \item
    What sort of errors are produced given different parameters?
  \item
    What parameters in the D-Flow FM model have the largest influence on
    errors related to numerical diffusion and dispersion?
  \item
    Are there indicators that predict the occurrence of numerical
    diffusion and dispersion in D-Flow FM?
  \end{enumerate}
\end{enumerate}

\subsection{Hypotheses}\label{hypotheses}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  There is significant numerical diffusion and negligible numerical
  dispersion in the D-Flow FM model when performing a lock-exchange
  experiment.

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    The order of errors is of 10E-4
  \item
    It is very sensitive to time and space related parameters and can be
    slightly improved by flow model parameters.
  \item
    Mostly numerical diffusion errors are produced except when more
    elaborate advection schemes are applied.
  \item
    The time step size, grid resolution and viscosity have the larges
    influence leverage on the accuracy of the model.
  \item
    Examples of such indicators are the dimensionless Reynolds and
    Froude numbers or the ratio between the net diffusivity coefficient
    in the model and the eddy
  \end{enumerate}
\end{enumerate}
